Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016

### 2020-04-06 anzjs_elections.Rmd
Small changes based on reviewer 2's second feedback

The older Australian population has often been considered to be more conservative, and the left leaning political parties (including Labor) have typically had a stronger appeal to younger people. This effect was indeed observed across the six elections, where populations between 20 and 34 years of age (`Pop_20_34`) aligned strongly with Labor preference (bottom row in Figure \@ref(fig:partresplot2)). Larger populations of 35 to 54 year olds (`Pop_35_54`) were also associated with Labor, but the magnitude of this effect was far smaller. Populations under 20 years of age was only significant in 2007, where `Pop_00_19` increased Liberal support.

@@

Higher proportions of single parent households were associated with Labor support in all elections (albeit insignificant in 2004, see row 6 in Figure \@ref(fig:partresplot2)), whereas the electoral family and household sizes (via the `FamHouseSize` variable) did not appear to be associated with either party.

@@

From 2007 onwards, both marriages (`Married`) and de facto relationships (`DeFacto`) were found to be strong predictors of the two-party preferred vote in favour of the Labor party. In 2001 and 2004 neither of these variables were significant (see rows 4 and 5 in Figure \@ref(fig:partresplot2)).

@@

This paper was produced using \textsf{RMarkdown} [@rmarkdown] and \textsf{knitr} [@knitr]. All corresponding code for this paper can be found in the github repository \url{github.com/jforbes14/eechidna-paper}, and the data used is available in the \textsf{eechidna} package [@eechidna]. All raw data was obtained from the Australian Electoral Commission, the Australian Bureau of Statistics and the Australian Government.

>>>>

The older Australian population has often been considered to be more conservative, and the left leaning political parties (including Labor) have typically had a stronger appeal to younger people. This effect was indeed observed across all six elections, as electorates with higher proportions of people aged between 20 and 34 (`Pop_20_34`) aligned strongly with Labor preference (bottom row in Figure \@ref(fig:partresplot2)). Larger proportions of 35 to 54 year olds (`Pop_35_54`) were also associated with Labor, but the magnitude of this effect was far smaller. Populations under 20 years of age was only significant in 2007, where `Pop_00_19` increased Liberal support.

@@

Higher proportions of single parent households were associated with Labor support in all elections (albeit insignificant in 2004, see row 6 in Figure \@ref(fig:partresplot2)), whereas family and household sizes (via the `FamHouseSize` variable) did not appear to be associated with either party.

@@

From 2007 onwards, proportions of both marriages (`Married`) and de facto relationships (`DeFacto`) were found to be strong predictors of the two-party preferred vote in favour of the Labor party. In 2001 and 2004 neither of these variables were significant (see rows 4 and 5 in Figure \@ref(fig:partresplot2)).

@@

This paper was produced using \textsf{R Markdown} [@rmarkdown] and \textsf{knitr} [@knitr]. All corresponding code for this paper can be found in the github repository \url{github.com/jforbes14/eechidna-paper}, and the data used is available in the \textsf{eechidna} package [@eechidna]. All raw data was obtained from the Australian Electoral Commission, the Australian Bureau of Statistics and the Australian Government.

### 2020-04-06 anzjs_elections.tex
Small changes based on reviewer 2's second feedback

The older Australian population has often been considered to be more conservative, and the left leaning political parties (including Labor) have typically had a stronger appeal to younger people. This effect was indeed observed across the six elections, where populations between 20 and 34 years of age (\texttt{Pop\_20\_34}) aligned strongly with Labor preference (bottom row in Figure \ref{fig:partresplot2}). Larger populations of 35 to 54 year olds (\texttt{Pop\_35\_54}) were also associated with Labor, but the magnitude of this effect was far smaller. Populations under 20 years of age was only significant in 2007, where \texttt{Pop\_00\_19} increased Liberal support.

@@

Higher proportions of single parent households were associated with Labor support in all elections (albeit insignificant in 2004, see row 6 in Figure \ref{fig:partresplot2}), whereas the electoral family and household sizes (via the \texttt{FamHouseSize} variable) did not appear to be associated with either party.

@@

From 2007 onwards, both marriages (\texttt{Married}) and de facto relationships (\texttt{DeFacto}) were found to be strong predictors of the two-party preferred vote in favour of the Labor party. In 2001 and 2004 neither of these variables were significant (see rows 4 and 5 in Figure \ref{fig:partresplot2}).

@@

This paper was produced using \textsf{RMarkdown} \citep{rmarkdown} and \textsf{knitr} \citep{knitr}. All corresponding code for this paper can be found in the github repository \url{github.com/jforbes14/eechidna-paper}, and the data used is available in the \textsf{eechidna} package \citep{eechidna}. All raw data was obtained from the Australian Electoral Commission, the Australian Bureau of Statistics and the Australian Government.

>>>>

The older Australian population has often been considered to be more conservative, and the left leaning political parties (including Labor) have typically had a stronger appeal to younger people. This effect was indeed observed across all six elections, as electorates with higher proportions of people aged between 20 and 34 (\texttt{Pop\_20\_34}) aligned strongly with Labor preference (bottom row in Figure \ref{fig:partresplot2}). Larger populations of 35 to 54 year olds (\texttt{Pop\_35\_54}) were also associated with Labor, but the magnitude of this effect was far smaller. Populations under 20 years of age was only significant in 2007, where \texttt{Pop\_00\_19} increased Liberal support.

@@

Higher proportions of single parent households were associated with Labor support in all elections (albeit insignificant in 2004, see row 6 in Figure \ref{fig:partresplot2}), whereas family and household sizes (via the \texttt{FamHouseSize} variable) did not appear to be associated with either party.

@@

From 2007 onwards, proportions of both marriages (\texttt{Married}) and de facto relationships (\texttt{DeFacto}) were found to be strong predictors of the two-party preferred vote in favour of the Labor party. In 2001 and 2004 neither of these variables were significant (see rows 4 and 5 in Figure \ref{fig:partresplot2}).

@@

This paper was produced using \textsf{R Markdown} \citep{rmarkdown} and \textsf{knitr} \citep{knitr}. All corresponding code for this paper can be found in the github repository \url{github.com/jforbes14/eechidna-paper}, and the data used is available in the \textsf{eechidna} package \citep{eechidna}. All raw data was obtained from the Australian Electoral Commission, the Australian Bureau of Statistics and the Australian Government.
